Compute Resilience EVI

### 2018-02-21 analysis/evi/compute_resilience_evi.Rmd
create means value of EVI previous, post and during

```{r packages, warning=FALSE, message=FALSE}
library('tidyverse')
library('stringr')
library('grid')
library('gridExtra')
library('pander')
source(paste0(di, '/script/R/eviResilience.R'))
```

```{r}
# Read data
iv <- read.csv(file=paste(di, "/data/evi_mean.csv", sep=""), header = TRUE, sep = ',')

@@

write.csv(aux_coefs, file=paste0(di, '/out/correla_resilience/correla_window_size.csv'), row.names = F)
```

@@

## Export and save 
```{r}
# Export csv 
write.csv(res3$evi, file=paste0(di, '/data/resilience/evi_period.csv'), row.names = FALSE)
write.csv(res3$resilience, file=paste0(di, '/data/resilience/resiliences.csv'), row.names = FALSE)
```

>>>>

```{r packages, warning=FALSE, message=FALSE}
library('tidyverse')
library('stringr')
library('grid')
library('gridExtra')
library('pander')
library('here')
source(paste0(di, '/script/R/eviResilience.R'))
```

```{r}
# Read data
iv <- read.csv(file=paste(di, "/data/evi/evi_mean.csv", sep=""), header = TRUE, sep = ',')

@@

write.csv(aux_coefs, file=paste0(di, '/out/correla_resilience/correla_window_size_evi.csv'), row.names = F)
```

@@

## Export and save 
```{r}
# Export csv 
write.csv(res3$evi, file=paste0(di, '/data/resilience/evi_period.csv'), row.names = FALSE)
write.csv(res3$resilience, file=paste0(di, '/data/resilience/resilience_evi.csv'), row.names = FALSE)
```

# Ver previos, during and post values of EVI 
```{r}

# add data of pop
anomalias <- read.csv(file=paste(di, "/data/anomalies/anomalias_evimean.csv", sep=""), header = TRUE, sep = ',')

attr_iv_malla_modis_id <- anomalias %>% dplyr::select(iv_malla_modi_id,long,lat,pop) %>% unique()

df <- res3$evi %>% inner_join(attr_iv_malla_modis_id, by='iv_malla_modi_id')

dfevi <- df %>% 
  mutate(
    clu_pop = as.factor(case_when(
      pop == 1 ~ "Camarate",
      pop %in% c(2,3,4,5) ~ 'Northern slope',
      pop %in% c(6,7,8) ~ 'Southern slope',
      pop == 9 ~ 'out')),
    clu_pop2 = as.factor(case_when(
      pop %in% c(1,2,3,4,5) ~ 'N',
      pop %in% c(6,7,8) ~ 'S',
      pop == 9 ~ 'out'))) %>% 
  filter(clu_pop != 'out')

# Change name of clu_pop2 and disturb_year 
dfevi <- dfevi %>% dplyr::rename(site = clu_pop2) %>% 
  mutate(disturb_year = as.factor(disturb_year)) %>% 
  mutate(disturb = case_when(
    disturb == "dr" ~ "1_dr",
    disturb == "pre" ~ "0_pre",
    disturb == "post" ~ "2_post"
  ))

# Get mean value of EVI for 2005 and 2012

dfevi_globalmeans <- dfevi %>% 
  group_by(disturb, disturb_year) %>% 
  summarise_at(c("mean_period"), 
               funs(mean(., na.rm = TRUE), sd(., na.rm=TRUE),se=sd(., na.rm=TRUE)/sqrt(n()))) %>% 
  mutate(site = "all") %>% as.data.frame()

dfevi_globalmeans_site <- dfevi %>% 
  group_by(disturb, disturb_year, site) %>% 
  summarise_at(c("mean_period"), 
               funs(mean(., na.rm = TRUE), sd(., na.rm=TRUE),se=sd(., na.rm=TRUE)/sqrt(n()))) %>% as.data.frame()

dfevi_all_globalmeans <- rbind(dfevi_globalmeans, dfevi_globalmeans_site)

write.csv(dfevi_all_globalmeans, file=here::here("data/evi", "evi_globalmeans_drouhgt.csv"),
          row.names = FALSE)

ggplot(dfevi_all_globalmeans, 
       aes(x=disturb, y=mean, colour=site)) + 
  geom_point(size=2) + 
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = .1) +
  geom_line(aes(group=site)) + 
  facet_wrap(~disturb_year) + 
  scale_x_discrete(labels = c("1_dr" = "Drought", "0_pre" = "Previous", "2_post" = "Posterior")) + 
  theme_bw() +
  xlab("") + ylab("EVI") + 
  theme(
    strip.background = element_rect(fill = "white"),
    strip.text = element_text(face="bold", size=12),
    axis.title.y = element_text(face="bold", size=12)
  ) +
  scale_color_manual(values=c('black', 'blue', 'gray'))

```
